```{r echo=FALSE,message=FALSE,warning=FALSE}
library(data.table)
library(stringr)
library(ripal)

p <- readPass(dumpfile)
p.info <- file.info(dumpfile)
p.bytes <- formatC(p.info$size, format="fg", big.mark = ",")
p.passCount <- nrow(p)
p.unique <- length(unique(p$orig))
p.top <- topPasswords(p)
b.top <- topBasewords(p)
p.byLen <- byLength(p)
p.byFreq <- lengthFreq(p)
p.charStats <- charStats(p)
p.common <- commonCounts(p) 

tot <- nrow(p)

kCounts <- function(ct) {
  tmp <- data.frame(Term=names(ct), Count=as.numeric(unlist(ct)))
  tmp$Percent <- ((tmp$Count / tot) * 100)
  kable(tmp[order(-tmp$Count),], row.names=FALSE)
}
```
ripal analysis of `r dumpfile` (file size: `r p.bytes` bytes)

Total entries: `r p.passCount`
Total unique entries: `r p.unique`

Top Passwords
```{r echo=FALSE,message=FALSE,warning=FALSE,results='asis'}
kable(p.top)
```

Top Basewords
```{r echo=FALSE,message=FALSE,warning=FALSE,results='asis'}
kable(b.top)
```

Password Length
```{r echo=FALSE,message=FALSE,warning=FALSE,results='asis'}
kable(p.byLen)
```

Password Length (by freq)
```{r echo=FALSE,message=FALSE,warning=FALSE,results='asis'}
kable(p.byFreq)
```

`r sprintf("One to six characters = %d, (%3.3f%%)", p.charStats$oneToSix, p.charStats$oneToSixPct)`
`r sprintf("One to eight characters = %d, (%3.3f%%)", p.charStats$oneToEight, p.charStats$oneToEightPct)`
`r sprintf("More than eight characters = %d, (%3.3f%%)", p.charStats$ninePlus, p.charStats$ninePlusPct)`

`r sprintf("Only lowercase alpha = %d, (%3.3f%%)", p.charStats$onlyLower, p.charStats$onlyLowerPct)`
`r sprintf("Only uppercase alpha = %d, (%3.3f%%)", p.charStats$onlyUpper, p.charStats$onlyUpperPct)`
`r sprintf("Only alpha = %d, (%3.3f%%)", p.charStats$onlyAlpha, p.charStats$onlyAlpha)`
`r sprintf("Only numeric = %d, (%3.3f%%)", p.charStats$onlyNumeric, p.charStats$onlyNumeric)`

`r sprintf("First capital last symbol = %d, (%3.3f%%)", p.charStats$firstCapLastSym, p.charStats$firstCapLastSymPct)`
`r sprintf("First capital last number = %d, (%3.3f%%)", p.charStats$firstCapLastNum, p.charStats$firstCapLastNumPct)`

Months
```{r echo=FALSE,message=FALSE,warning=FALSE,results='asis'}
kCounts(p.common$months)
```

Months (abbrev)
```{r echo=FALSE,message=FALSE,warning=FALSE,results='asis'}
kCounts(p.common$monthsAbbrev)
```

Weekdays
```{r echo=FALSE,message=FALSE,warning=FALSE,results='asis'}
kCounts(p.common$weekdays)
```

Weekdays (abbrev)
```{r echo=FALSE,message=FALSE,warning=FALSE,results='asis'}
kCounts(p.common$weekdaysAbbrev)
```

Worst 25 Passwords Counts
```{r echo=FALSE,message=FALSE,warning=FALSE,results='asis'}
kCounts(p.common$worst)
```

Planets
```{r echo=FALSE,message=FALSE,warning=FALSE,results='asis'}
kCounts(p.common$planets)
```

Common Colors
```{r echo=FALSE,message=FALSE,warning=FALSE,results='asis'}
kCounts(p.common$colors)
```

Seasons
```{r echo=FALSE,message=FALSE,warning=FALSE,results='asis'}
kCounts(p.common$seasons)
```

Years
```{r echo=FALSE,message=FALSE,warning=FALSE,results='asis'}
kCounts(p.common$years)
```


